---
title: "Homework 1, Part 2"
author: "Ugne Jankauskaite"
date: "2017-09-24"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R markdown exercise 

### Sampling from log-normal distribution

**1.** Sample 100 values from log-normal distribution with mean 1 and variance 0.25.

```{r sample}
set.seed(560)# for reproducibility
x <- rlnorm(100, 1, .25) #sample size, mean, variance
```

**2.** Sample mean:

```{r mean}
mean(x)
```

**3.** Sample variance:

```{r variance}
var(x)
```

\newpage

### Histogram

**1.** Histogram of the distribution:

```{r histogram, }
hist(x, main="Histogram for log-normal distribution", col="blue")
```

\newpage

**2.** Histogram of the distribution on the log scale:

```{r logHistogram, }
h = hist(x, plot=F)
h$counts = log10(h$counts)
plot(h, main="Histogram for log-normal distribution on log scale", col="blue", ylab='log10(Frequency)')
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
